Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-04-01 documents/cpm.tex
commit discussion

The second general idea about data-driven modeling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
  target star.
In what follows, we are going to use input data both from pixels of other stars and the  
target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, 
which is optimal for exoplanet transit searching.

@@

\Bernhard{Hogg: maybe you want to add sth about the device being 'self-calibratable'?}

@@

where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? 
  If not estimated, how do we know them?} individual-pixel noise variances, and $\lambda_{a}$, 
  $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{m,n,m'}, b_{m,n,v}$. 
  In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, 
  because in \name\ the $\chi^2$ minimization for every time
  point is independent and the third index--$n$ indicates 
  which time point the prediction $I^{\ast}_{m,n',n}$ is being trained for, 
  the detail of the independent $\chi^2$ minimization will be discussed below.

@@

However, forget all the unsolved problems, 
  we expect that data-driven model like our method will enable astronomical discoveries 
  at higher sensitivity on the existing \Kepler\ data as well as on future missions.  
As we know, \Kepler\ \project{K2} \citep{k2} data are suffering from the broken-down of reaction wheels, 
  which makes the satellite hard to control and introduce significant systematics. 
Flexible data-driven model \citep{dfm} has already shown the power on the \project{K2} data 
  and find new planets.
Moreover, in 2017, NASA is planning the launch of another space telescope---
  \project{TESS} (Transiting Exoplanet Survey Satellite, \cite{tess}), 
  which will perform an all-sky survey for small (earth-like) planets of nearby M stars. 
  We think our method can be simply extended for these project to help achieving higher precession and more scientific results.

>>>>

The second general idea about data-driven modelling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
  target star.
In what follows, we are going to use input data both from pixels of other stars and the  
target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, 
which is optimal for exoplanet transit searching.

@@

We also want to emphasis that all the calibration in this paper for \Kepler is 
  based on the assumption that the device is 'self-calibratable', 
  which means all the information we need to calibrate the device are contained in the device itself 
  (either in science data or engineering data) and no external information, 
  for example, measurements from other device, are needed

@@

where the $\sigma^2_{m,n'}$ are the (the column FLUX\_ERR in TPF is used, which is a image of 1-sigma error provided by the Kepler team) individual-pixel noise variances, and $\lambda_{a}$, 
  $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{m,n,m'}, b_{m,n,v}$. 
  In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, 
  because in \name\ the $\chi^2$ minimization for every time
  point is independent and the third index--$n$ indicates 
  which time point the prediction $I^{\ast}_{m,n',n}$ is being trained for, 
  the detail of the independent $\chi^2$ minimization will be discussed below.

@@

One possible way to solve this kind of edge effect 
  but still preserve the transit signals to do the simultaneous fitting 
  for both systematics and transit signal together, 
  like what have been done in \cite{dfm}. 
That is,  
  instead of only modelling the systematics% 
  and then subtracting it from the raw data to produce some de-trended lightcurves,
  a comprehensive model for both all components in the data (systematics, stellar variabilities and transits)  can be made. In this kind of model, there is no need for train-and-test framework,
  since all transit signals have already been modelled 
  and no de-trended lightcurve will be produced. Planets will be found directly in the model itself.

However, despite all the problems mentioned in the \name,
  we expect that data-driven model like our method will enable astronomical discoveries 
  at higher sensitivity on the existing \Kepler\ data as well as on future missions.  
As we know, \Kepler\ \project{K2} \citep{k2} data are suffering from the broken-down of reaction wheels, 
  which makes the satellite hard to control and introduce significant systematics. 
Flexible data-driven model \citep{dfm} has already shown the power on the \project{K2} data 
  and find new planets.
Moreover, in 2017, NASA is planning the launch of another space telescope---
  \project{TESS} (Transiting Exoplanet Survey Satellite, \cite{tess}), 
  which will perform an all-sky survey for small (earth-like) planets of nearby M stars. 
  We think our method can be simply extended for these project to help achieving higher precession and more scientific results.
